%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Biomedical Eng. PhD Student | Researcher} % Job title
    {Instituto de Telecomunicações} % Organization
    {Lisbon, Portugal} % Location
    {Jan. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item[]\textbf{Emotion Recognition}
        \item{Developmed Machine Learning algorithms for emotion recognition based on multimodal physiological data with superior to comparable results to the state-of-the-art for selected datasets (SJR: Q2; IF: 3.847 [1]). Survey of the field (SRJ: Q1; IF: 3.9 [2]).}
        \item {Developed feature extraction libraries (time, frequency, time-frequency, cepstral, phase-space) available at BioSPPy, a Python toolbox for biosignal processing (SRJ: Q2; IF: 3.4 [3], under review).}
        \item {Created a real-world dataset for group emotion recognition based on physiological data, containing 31 movie sessions, 380+ hours of data from over 190 subjects. (SJQ: Q1; IF: 9.8 [4]).}
        \item[] \textbf{Back-end Development}
        \item {Developed of WiFi and Bluetooth communication module for group data collection and storage using: ScientISST, BITalino, BITalino R-IoT, and FMCI XinhuaNet devices. Reported multimodal physiological data collection using 20 devices at 25 Hz and 10 devices at 60 Hz (SJR: Q1; IF: 5.606 [5]).}
        \item[] \textbf{Front-end Development}
        \item {Developed an user graphical interface to observe and annotate physiological data in real‑time (SJR:Q1; IF: 13.99 [6], under review).} 
        \item[]\textbf {MSc and BSc Students Supervision}
        \item {Co-supervised over 3 MSc thesis and 9 BSc projects. Four papers published (2 Q1, 1 Q1 under revision and 2 Int'l Conf.).}
        %\item[] \textbf{Showcases}
        %\item {Dissemination of FMCI Xinhuanet data collection devices at 2019 Web Summit, Lisbon. Outreach activity and demonstration interface of the device working in real-time.}
        %\item {DataWe: A neurocinematic system for studying collective decision-making. Developed the back-end infrastructure for group physiological data collection. Project in collaboration with Tallinn University. Displayed at European Commission Joint Research Centre Ispra Sector, Italy.}
        %\item {Online theatre as a research instrument. Developed the back-end infrastructure for group physiological data collection. Project in collaboration with Univ. of Tartu.}
      \end{cvitems}
    }
%--------------------------------------------------------- 
\cventry
{Logistics Coordinator} % Job title
{ScientISST - Biomedical Engineering Student Group} % Organization
{Lisbon, Portugal} % Location
{Jan. 2022 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item[] {\textbf{Operations Coordinator}}
    \item {Managed the instrumentation inventory.}
    \item[] {\textbf{Outreach}}
    \item {Organized and participated in 10+ outreach activities (scientific fairs, instagram posts, lab visits).}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Visiting Student working on Emotion Recognition using Deep Learning} % Job title
{Centrum Wiskunde \& Informatica} % Organization
{Amsterdam, Netherlands} % Location
{Jan. 2022 - Jul. 2022} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed novel interpersonal weighted group synchrony approach for emotion recognition, surpassing previous work for K-EmoCon dataset on arousal, and providing a new baseline on AMIGOS for long-videos (SJR:Q1; IF: 13.99 [7]).}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Research Assistant on Machine Learning} % Job title
{Fraunhofer Portugal} % Organization
{Lisbon, Portugal} % Location
{Feb. 2018 - Jan. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented Semi-Supervised Active Learning for Human Activity Recognition algorithms based on smartphone inertial sensors, reducing the annotated data by 89+\% while maintaining an accurate performance (SJR: Q1; IF: 3.847 [8]).}
    \item {Developed TSFEL - a library for time series feature extraction and selection (SRJ: Q2; IF: 3.4 [9]).}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
