%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cventry
{} % Job title
{} % Organization
{} % Location
{} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {[1] \textbf{P. Bota}, C. Wang, A. Fred, and H. Silva, “Emotion assessment using feature fusion and decision fusion classification based on physiological data: Are we there yet?,” Sensors, vol. 20, no. 17, p. 4723, 2020. SJR: Q2; IF: 3.847} 
    \item {[2] \textbf{P. Bota}, C. Wang, A. L. N. Fred, and H. Plácido Da Silva, “A review, current challenges, and future possibilities on emotion recognition using machine learning and physiological signals,” IEEE Access, vol. 7, no. 1, pp. 140990–141020, 2019. SJR: Q1; IF: 3.9}
    \item {[3] \textbf{P. Bota}, R. Silva, C. Carreira, A. Fred, and H. P. da Silva, “BioSPPy: A python toolbox for physiological signal processing,” SoftwareX, vol under revision 2023. SJR: Q2; IF: 3.4}
    \item {[4] \textbf{P.Bota}, J.Brito, A.Fred, P.Cesar, and H.Silva,“A real-world dataset of group emotion experiences based on physiological data,” Scientific Data, vol. in press, 2023. SJR: Q1; IF: 9.8}
    \item {[5] \textbf{P. Bota}, E. Flety, H. P. d. Silva, and A. Fred, “EmotiphAI: a biocybernetic engine for real-time biosignals acquisition in a collective setting,” Neural Computing and Applications, vol. 35, no. 8, pp. 5721–5736, 2023. SJR: Q1; IF: 5.606}
    \item {[6] \textbf{P. Bota}, P. Cesar, A. Fred, and H. Silva, “Exploring retrospective annotation in long-videos for emotion recognition,” IEEE Trans. on Affective Computing, vol. under revision, 2023. SJR: Q1; IF: 13.99}
    \item {[7] \textbf{P. Bota}, T. Zhang, A. El Ali, A. Fred, H. P. da Silva, and P. Cesar, “Group synchrony for emotion recognition using physiological signals,” IEEE Transactions on Affective Computing, 2023. SJR: Q1; IF: 13.99}
    \item {[8] \textbf{P.Bota}, et al. "A semi-automatic annotation approach for human activity recognition." Sensors 19.3 (2019): 501. SJR: Q1; IF: 3.847}
    \item {[9] M. Barandas, D. Folgado, L. Fernandes, S. Santos, M. Abreu, \textbf{P. Bota}, H. Liu, T. Schultz, H. Gamboa "TSFEL: Time series feature extraction library." SoftwareX 11 (2020): 100456. SJR: Q2; IF: 3.4}
  \end{cvitems}
}
%\\
%[8] 
%---------------------------------------------------------

