%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
PhD finalist in Biomedical Engineering at Univ. of Lisbon (ULisboa), Instituto Superior Técnico (IST) and researcher at Instituto de Telecomunicações (IT), with around 6 years of research experience.

My PhD focused on developing artificial intelligence algorithms for emotion recognition from physiological signals, which resulted in a strong publication record with 10+ papers in peer-reviewed journals (8 in Q1, 2 in Q2, 3 under revision). 

Additionally, my PhD journey has been marked by contributions to over 15+ collaborations (6 international, 9 national), 5+ workshops (including a NATO talk), and 5+ scientific fairs.

Besides scientific output, my work includes the end-to-end development of EmotiphAI, a platform for group physiological data collection in an audience, showcased at the 2019 WebSummit, at the European Commission's Resonances III Fest. and an online theatre in collaboration with Univ. Tartu. This project underlined my multi-faced skills in software architecture, front-end and back-end, and reflected my commitment to learning and applying new technologies.
\end{cvparagraph}
